Stable Hot Spot Analysis (Draft)

### 2017-06-13 paper-main.tex
First version of Results

% extent
The two datasets (morning and evening flights) depicted in
Fig.~\ref{fig:ComparisonMorning} and Fig.~\ref{fig:ComparisonEvening} were
obtained from a thermal flight over the city of Karlsruhe on 26.09.2008 at
6:30--7:45 and 20:00--21:30. The flights were executed by the
Nachbarschaftsverband
Karlsruhe\footnote{http://www.nachbarschaftsverband-karlsruhe.de/}. A single
pixel in the raster represents an area of approximately $5{\times}5m$. The whole
dataset of size $35{\times}25\,km$ was cropped into the inner city area of
$2.4{\times}1.4\,km$. % temp range
The temperatures in our dataset range from -1.7°C to 18.3°C.
% missing values = NAs
Missing values in the dataset were interpolated using a focal median function
with a square matrix of 11x11 pixels, mainly for speeding up further
computations and to avoid special handling of NA values.

@@

\section{Results}
\subsection{Heatmap}
\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{FocalRelation}
    \includegraphics[width=\linewidth]{images/FocalRealationUp}
    \label{fig:FocalRelation}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{WeightRealtion}
    \includegraphics[width=\linewidth]{images/WeightRelationUp}
    \label{fig:WeightRealtion}
  \end{subfigure}
  \caption{Heatmap of Relation between size of weight matrix $W$ and focal matrix $F$}
  \label{fig:RealtionUp}
\end{figure}

@@

The results for the hot spot analysis are found in
Fig.~\ref{fig:ComparisonMorning} and Fig.~\ref{fig:ComparisonEvening} for a
comparison of $G^*$ and the Focal $G^*$ statistic. It can easily be seen that
both versions produce similar results, but the focal versions produces a more
differentiated picture for larger weight matrices. Small differences on a
global scale are more pronounced on a regional scale and result in smaller and
finer areas for hot spots. This enables the detection of additional hot spots
and interesting areas which are most easily observable for the weight matrix of
size $7{\times}7$ in the evening (Fig.~\ref{fig:ComparisonEvening}). This
enables the detection of significant deviations from the surrounding area. 
In contrast the Standard $G^*$ statistic shows larger areas as important.
Therefore, depending on the need of a planner, the Focal $G^*$ statistic
is more helpful to identify individual areas of interest whereas the standard
$G^*$ statistic gives a more broad overview. For the identification of IUHI this
is quite important. As a city planer wishes to detect critical areas, it is
important to detect not only general hot areas, but also those points where the
most extreme differences in a local context exist. Finding those areas can help 
identify the underlying reasons or plan individual solutions.

Based on these images one can also see that the hot spots found by the Focal
$G^*$ statistic seem to be more stable. We compare their stability using only
the $ SoH^\uparrow$ for lack of space. A plot of the results can be found in
Fig.~\ref{fig:EvalResults}. Fig.~\ref{fig:EvalResults} compares the $
SoH^\uparrow$ between each increasing size of the weight matrix W. At a first
glance, one can see that the typical implementation with a square weight matrix
is the most unstable hot spot analysis, regardless of time of day. This is to be
expected as the binary weights increase the dependence on the weight matrix. The
use of a decreasing weight matrix perform better. As the more outlying data
points get less weight, this reduces the dependence on the weight matrix and
leads therefore to more stable results. Our proposed Focal $G^*$ statistic
achieves the most stable results in almost all cases. Only data points in a
restricted region around the area of interest may influence the significance
result. Through this restriction high values at key points gains more weight
regardless of the weight matrix and are therefore more independent of the weight
matrix. This increases the stability. The decrease in stability for the largest
weight matrices is most likely a result of the parametrization of the focal
matrix. With increasing size of the weight matrix in relation to the focal
matrix the value of each pixel is approaching to the mean of the area of the
weight matrix. As can be easily seen from Def.~\ref{def:GenericGetisOrdFunc}
then the value for every pixel would be zero.

>>>>

Our results are based on the cab taxi data set from New York, Manhattan \cite{TODO}. 
We used only the dataset of January 2016. From that
dataset we used the $pickup_longitude$ and $pickup_latitude$ column. 
The borders of the raster are between (40.699607, -74.020265) and (40.769239, -73.948286). 
Zoom size 1 means we aggregate every point, which was in range of 100x100*0.000001 into one pixel. 
In zoom size N we aggregated NxN pixel from zoom size 1 into a new pixel.
%
For our measurements we specified the following data series:
\begin{itemize}
 \item The weight matrix W is from 3 to 43 with a stepsize of 4.
 \item The focal matrix F is from  17 to 125 with a stepsize of 12.
 \item The zoom level is from 1 to 5 with a stepsize of 1.
\end{itemize}
Therefore we calculate around 10*10*5=500 results for each fixed x.
The following conditions must hold F>W, F<Raster.cols und F<Raster.rows.

@@

\section{Results}

\subsection{Heatmap}
\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{FocalRelation}
    \includegraphics[width=\linewidth]{images/FocalRealationUp}
    \label{fig:FocalRelation}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{WeightRealtion}
    \includegraphics[width=\linewidth]{images/WeightRelationUp}
    \label{fig:WeightRealtion}
  \end{subfigure}
  \caption{Heatmap of Relation between size of weight matrix $W$ and focal matrix $F$}
  \label{fig:RealtionUp}
\end{figure}

@@

% Focal size  
%	Increase of focal size leads to better results in the upward property
% 	Standard deviation decrease with higher focal size 
%	No standard deviation af F 17x17 because of missing clusters
%	The downward property reaches its maximum at 65x65
%
%	Conclusion: F should be around 65x65 or higher
In figure ~\ref{TODO Up} you can see that an increase of the focal size leads to better results for $SoH^{\uparrow}$. 
The standard deviation decreases also with a higher focal size. Only 
at focal size F of 17x17 there is no standard deviation. At focal size F 17x17 the standard deviation is 
missing, because the weight size W must be smaller than F. When F and W have similar
size, there are no clusters. (TODO assumtion for SOH, if no clusters we asume Up/Down = 0)
$SoH^{\downarrow}$ in figure ~\ref{TODO Down} reaches its maximum for focal size F 65x65 in the regarded area.
%
% Weight size
%	Increase of weight leads to increase of downward property
%	Small break downs for G* for upward and downward property
%	For the upward property Focal G* is better than G*
%
%	Conclusion: Higher weight size leads to better results. There are parametrisations of Focal G* which are better than G*
In figure ~\ref{TODO wDown} one can see that an increase of the weight size leads to better results.
Focal $G^*$ is not allways better than $G^*$ which would be a perfect result we hoped for. But it seems 
that $G*$ has at 23 and 39 some parametrisation which leads to small break downs. 
The standard deviation is in this area higher than in the other points.
In figure ~\ref{TODO wUp} the break downs are also visible.
The high standard deviation indicates that it is possible to use this parametrisation for better results
The $SoH^{\uparrow}$ in ~\ref{TODO wUp} is mostly better than $G^*$ which was our conclusion in \ref{TODO last paper}.
%
% Zoom
%	G* alwas better than Focal G* for upward and downward property
%	Focal G* has different focal sizes because zoom is compared
%	At zoom level 4 G* increase much more than Focal G*
%
%	Conclusion: G* is better than Focal G* in the zoom dimension, but the focal size is fixed. The zoom dimension has the least 
%	influence on the value
The last variation we examined was the zoom level. One can see that $G^*$ is always better than Focal $G^*$.
The target area of Focal $G^*$ increases if you zoom out.
